Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-08 manuscript.tex
new figures
add simulation plotter for variations

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

\begin{prop}
    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \bar\tau_d$.
    \label{prop:dis_bound}
\end{prop}

In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
\begin{assum}
    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
    \label{assum:feasible}
\end{assum}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.

To overcome this issue, a DNN is employed to approximate $\rbu^*$.
Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.

In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
\begin{align}
    \rbu^*=& \idealNN+\mv\epsilon,
    \label{eq:control:ideal}
\end{align}
which is estimated online by
\begin{align}
    \rbu =& \estNN,
    \label{eq:control:est}
\end{align}
where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.

Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $V_1$ can be rewritten as
\begin{equation}
    \ddtt{V}_1
    \le 
    -\lambda_{\min}(\mm K)\norm{\fe}^2
    +
    \bar\tau_d\norm{\fe}
    +
    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
    .
    \label{eq:lya1:dot2}
\end{equation}
Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).

@@

The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top \q_{NN},
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k,
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1,
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
        &
        i = 0,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
    \pptfrac{\fe}{\rbu}
    \approx
    [
        \mysign(\pptfrac{r_i}{\tau_j})
    ]_{i,j\in[1,\cdots,m]}
$ using the sign of each entry (\ie control direction).
However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\alpha 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

%% ALGORITHM PART; Now omitted!
% The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.

@@

As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
\begin{equation}
    \Theta_{\fe}^{c_1} 
    = 
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\min}(\mm K)}
    \right\}
    .
    \label{eq:invariant:c1:fe}
\end{equation}

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\bar\tau+\bar\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

>>>>

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
    =
    \mysat(\rbu)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the control input. 
The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

@@

\begin{prop}
    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \overline\tau_d$.
    \label{prop:dis_bound}
\end{prop}

In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
\begin{assum}
    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
    \label{assum:feasible}
\end{assum}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{src/figures/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.

To overcome this issue, a DNN is employed to approximate $\rbu^*$.
Let $\NN:=\NN({\q}_n;\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of $\NN({\q}_n;\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.

In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
\begin{align}
    \rbu^*=& \idealNN+\mv\epsilon,
    \label{eq:control:ideal}
\end{align}
which is estimated online by
\begin{align}
    \rbu =& \estNN,
    \label{eq:control:est}
\end{align}
where $\hat\NN:=\NN({\q}_n;\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.

Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $V_1$ can be rewritten as
\begin{equation}
    \ddtt{V}_1
    \le 
    -\lambda_{\min}(\mm K)\norm{\fe}^2
    +
    \overline\tau_d\norm{\fe}
    +
    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
    .
    \label{eq:lya1:dot2}
\end{equation}
Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k,
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1,
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes {\q}_n^\top  ), 
        &
        i = 0,
    \end{cases}
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\Gamma \pptfrac{L}{\estwth}
            =
            -\Gamma 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{j\in\mathcal{I}}
                \lambda_j 
                \pptfrac{c_j}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_j
            & 
            = 
            \beta_j\pptfrac{L}{\lambda_j} 
            = 
            \beta_j c_j ,
            \quad \forall j\in\mathcal I,
        \label{eq:adap:lbd}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}
\end{subequations}
where $\Gamma=\Gamma^\top:=\mydiag([\gamma_1,\cdots,\gamma_n])\in\R^{n\times n}_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity. 
By selecting $\gamma_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.

@@

In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
    \pptfrac{\fe}{\rbu}
    \approx
    [
        \mysign(\pptfrac{r_i}{\tau_j})
    ]_{i,j\in[1,\cdots,m]}
$ using the sign of each entry (\ie control direction).
However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
\begin{equation}
    \ddtt{\estwth}
    \approx
    -\Gamma 
    \left(
        \pptfrac{\estNN}
        {\estwth}^\top
        \fe
        +
        \textstyle\sum_{j\in\mathcal{I}}
        \lambda_j 
        \pptfrac{c_j}{\estwth}
    \right)
    .
    \label{eq:adap:th:approx}
\end{equation}

%% ALGORITHM PART; Now omitted!
% The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\Gamma$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \overline\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.

@@

As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as w
\begin{equation}
    \Theta_{\fe}^{c_1} 
    = 
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{2\overline\tau+\overline\tau_d}{\lambda_{\min}(\mm K)}
    \right\}
    .
    \label{eq:invariant:c1:fe}
\end{equation}

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2}\estwth_k^\top\Gamma^{-1} \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        \Gamma^{-1}\Gamma
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}
